---
title: "hw8"
author: "Siwei Tang"
date: '2022-03-29'
output:
  html_document: default
  pdf_document: default
---
# Q1
## a
$$\hat{Y}=\begin{cases}
0 & \text{ if } x= 0\\
1 & \text{ if } x= 1\\
1 & \text{ if } x= 2
\end{cases}$$
```{r}
(-2 -1)^2 * 1/6 + (2-1)^2*1/2
```
MSPE $=\mathbb{E}((Y-\hat{Y})^2) = 2$

## b
```{r}
muy = c(-2,0,1,2) %*% c(1/6,1/6,1/6,1/2)
mux = c(2,0,1,2) %*% c(1/6,1/6,1/6,1/2)
varx = c(4,0,1,4) %*% c(1/6,1/6,1/6,1/2) - mux^2
# when y >= 0
covxy = c(2*-2,0,1,4) %*% c(1/6,1/6,1/6,1/2) - muy * mux
cat("mux is:",mux,";muy:",muy,"cov(x,y):",covxy,'\n')
cat("Y hat is " ,muy + (covxy * (-mux)/varx), "+",covxy/varx,"X")
yhat2 = as.vector(muy + (covxy * (-mux)/varx) + covxy/varx*c(0,1,2))
yhat2 
```

$\hat{Y} = \mu_Y Y+\Sigma(Y,X)\Sigma(X)^{-1}(X-\mu_X)$\\
$\hat{Y} = 0.1904762 + 0.4285714 X$
$$\hat{Y}=\begin{cases}
0.1904762  & \text{ if } x= 0\\
0.6190476 & \text{ if } x= 1\\
1.0476190 & \text{ if } x= 2
\end{cases}$$
```{r}
# calculating MSPE
mspe = c(0.1904762^2, (1- 0.6190476)^2, (2 - 1.0476190)^2,
         (-2 - 1.0476190)^2) %*% c(1/6,1/6,1/2,1/6)
cat("MSPE:",mspe)
```
## c
Because the MSPE is optimal when $\mu_x = \mu_y = 0$. We didn't center R.V. X and Y.

# Q2
## a
$\gamma(k) = cov(Y_t,Y_{t-k}) = cov(\phi_1(Y_{t-1}-\mu)+\phi_2(Y_{t-2}-\mu)+\epsilon_t,Y_{t-k})\\$
$= cov(\phi_1Y_{t-1},Y_{t-k})+cov(\phi_2Y_{t-2},Y_{t-k}) + 0\\$
$= \phi_1\gamma(k-1) + \phi_2\gamma(k-2)\\$

Divide $\gamma(0)$ on both left side and right side, gives us

$\rho(k) = \phi_1\rho(k-1) + \phi_2\rho(k-2)\\ \square$

## b
Because $\rho(0) = 1$ for time series sequence $Y_t, \forall t$
Applying the result when k =1 and 2 gives us
$\rho(1) = \rho(0)\phi_1 +\rho(1)\phi_2$
$\rho(2) = \rho(1)\phi_1 +\rho(0)\phi_2$
Therefore ($\phi_1,\phi_2$) solves this linear system. $\square$

## c
```{r}
rho = matrix(c(.3,.2),nrow = 2, ncol =1)
sqr_mtx = matrix(c(1,.3,.3,1), 2,2)
res = solve(sqr_mtx) %*% rho
print(res)
phi1 = res[1]
phi2 = res[2]
phi3 = c(.2,.3) %*% res
cat("Phi1 is",phi1,"\nPhi2 is",phi2,"\n")
cat("Phi3 is",phi3)
```
# Q3
## 1
```{r}
library(stats)
library(ggplot2)
library(forecast)
library(FitAR)
root = './datasets/'
file = paste(root,'RUT_03_2015-03_2019.csv', sep ="")
df = read.csv(file)
n = dim(df)[1]
r = df$Adj.Close[-1]/df$Adj.Close[-n] - 1
acf(as.vector(r), lag =20)
# box-Ljng test
Box.test(r, lag = 10, type = "Ljung-Box")
```

The p-value of Box-Ljung test is 0.3124, which indicates that we cannot reject the null hypothesis. So we have accept the null that the auto correlation are all zeros out to lag 10. From the ACF plot, we dont see any big violations of autocorrelation within the 95% confidence interval till lag = 20. This shows that there is no strong auto-correlation on the sequence. 
## b
```{r}
RUT_ar = ar(r, aic= TRUE, order.max = 6, method = "mle")
RUT_ar
# fit the model with ARIMA
RUT_arima = arima(r, order = c(4,0,0),
                  method = "ML")
temp_df = data.frame(X = RUT_arima$residuals)
p <- ggplot(temp_df, aes(sample = X))
p + stat_qq() + 
  stat_qq_line()+
  labs(title = "QQ plot of reisiduals",
       x = "Theoretical quantile",
       y = "Sample quantile")
# Box_Ljung test
Box.test(residuals(RUT_arima), lag = 10, type = "Ljung-Box", fitdf = 4)
acf(as.vector(residuals(RUT_arima)), lag =10, main = "ACF of Residuals")
LBQPlot(residuals(RUT_arima))
checkresiduals(RUT_arima)
# auto.arima(r, max.p = 20,max.q = 0,d=0 ,ic = "aic")
```

The AR model picks the order `p = 4`. Numerical test of Box-Ljung indicates that 
with order p = 4, lag = 10 , there is no auto-correlation in the residuals. Graphic 
plot on Box-Ljung test shows that all p-values are above the 95% interval, which 
means there is no correlation left in the model.The QQ plot on the residuals shows
a bad approximation on its normality, as most of the points locate along the line.
But its worth noticing that the residuals are heavy tailed, which means it has more 
density on its tails.

## c
```{r}
library(tseries)
f = forecast(RUT_arima, h =12)
n = dim(df)[1]
new_date = seq.Date(as.Date(df$Date)[n], length = 12, by = "week")
upper = f$upper[13:24]
lower = f$lower[13:24]
temp = data.frame(Date = new_date, lower = lower, upper = upper, y = f$mean)
new_date = append(df$Date,as.character(new_date))[-1]
new_return = c(r, f$mean)
new_df = data.frame(Date = new_date, y = new_return)
p = ggplot(new_df) +
  geom_line(aes(as.Date(Date), y),
            color = "black",
            size  = 0.5)+
  geom_line(data = temp,
                          aes(Date, y),
                          color = "red",
                          size  = 1) + 
  geom_ribbon(aes(x = as.Date(Date), ymin = c(r,lower), 
                  ymax = c(r, upper)),
              fill = "grey70", alpha = 0.5)+
  labs(title = "AR p = 4 Prediction on Return",
       x = "Date",
       y = "Return")
p
print(temp)
```
## c
```{r}
arma(r)
arma_fit = arima(r, order = c(1,1,0),method = "ML")
checkresiduals(arma_fit)
Box.test(residuals(arma_fit), lag = 10, type = "Ljung-Box", fitdf = 2)
LBQPlot(residuals(arma_fit))
```

`Arma` reuslt  shows that the best pick for order is `p = 1, q = 1`, and the residuals
plot implies a bad fit because most of the points are below the 95% interval.
In addition, the ACF plot shows strong auto-correlation when lag is small. 
Residuals doesn't have normalty as well, it's quite right skewed.
In summary, ARMA model is not a good fit.
## e
```{r}
library(tseries)
f = forecast(arma_fit, h =12)
n = dim(df)[1]
new_date = seq.Date(as.Date(df$Date)[n], length = 12, by = "week")
upper = f$upper[13:24]
lower = f$lower[13:24]
temp = data.frame(Date = new_date, lower = lower, upper = upper, y = f$mean)
new_date = append(df$Date,as.character(new_date))[-1]
new_return = c(r, f$mean)
new_df = data.frame(Date = new_date, y = new_return)
p = ggplot(new_df) +
  geom_line(aes(as.Date(Date), y),
            color = "black",
            size  = 0.5)+
  geom_line(data = temp,
                          aes(Date, y),
                          color = "red",
                          size  = 1) + 
  geom_ribbon(aes(x = as.Date(Date), ymin = c(r,lower), 
                  ymax = c(r, upper)),
              fill = "grey70", alpha = 0.5)+
  labs(title = "AR p = 4 Prediction on Return",
       x = "Date",
       y = "Return")
p
print(temp)
```







